Breast Cancer Diagnosis Classification Analysis

### 2022-12-09 ethan_temp_powerpoint.rmd
Add files via upload
Ethan edits to powerpoint

---
title: "Breast Cancer Diagnosis Classification Analysis"
author: Austin Lackey, Ethan Powers and Danny Laposata
date: "December 9th, 2022"
output: 
  powerpoint_presentation: 
    reference_doc: template.pptx

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(caret)
library(leaps)
library(caTools)
library(tidymodels)
library(glmnet)
library(pls)
library(forecast)
library(GGally)
library(plyr)
library(readr)
library(repr)

set.seed(420)

dataTemp <- read.csv("breast_cancer_diagnostic_data.csv")
datatemp2 <- dataTemp %>% select_if(~ !any(is.na(.)))
dataTot <- datatemp2[,!names(datatemp2) %in% c("id")]

traintemp <- read.csv("training.csv")
trainTot <- traintemp[,!names(traintemp) %in% c("id")]

knitr::opts_chunk$set(fig.width=12, fig.height=8) 
```

@@

## Features
- Radius: Average Distance from cell center to cell perimeter
- Texture: Standard deviation of gray-scale values; brightness of pixel of cell
- Perimeter: Distance around nucleus boundary
- Area: Area of the nucleus
- Smoothness: Variation in cell's radial lengths
- Compactness: The Perimeter^2/Area
- Concavity: Size of the indention in nucleus boundary
- Concave Points: Number of points on indented section of nucleus boundary
- Symmetry: Deviation of the nuclei shape from the ideal measurement
- Fractal Dimension: Measurement of irregularity in nucleus boundary

@@

This is my validation plot
```{r}
dataE <- dataTot
corr_df <- dataE[,c('area_worst', 'area_mean', 'concave.points_mean', 'radius_worst')]
ggpairs(corr_df)
```

## Model Assesments

>>>>

---
title: "Breast Cancer Diagnosis Classification Analysis"
author: "Austin Lackey, Ethan Powers and Danny Laposata"
date: "December 9th, 2022"
output:
  powerpoint_presentation:
    reference_doc: template.pptx
  slidy_presentation: default
always_allow_html: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(caret)
library(leaps)
library(caTools)
library(tidymodels)
library(glmnet)
library(pls)
library(forecast)
library(GGally)
library(plyr)
library(readr)
library(repr)
library(knitr)
library(kableExtra)

set.seed(420)
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
```

@@

## Variable Descriptions
- Radius: Average Distance from cell center to cell perimeter
- Texture: Standard deviation of gray-scale values; brightness of pixel of cell
- Perimeter: Distance around nucleus boundary
- Area: Area of the nucleus
- Smoothness: Variation in cell's radial lengths
- Compactness: The Perimeter^2/Area
- Concavity: Size of the indention in nucleus boundary
- Concave Points: Number of points on indented section of nucleus boundary
- Symmetry: Deviation of the nuclei shape from the ideal measurement
- Fractal Dimension: Measurement of irregularity in nucleus boundary

@@

- Austin Top 5 Importance Variables
    - *area_mean
    - *area_worst
    - *concave.points_mean
    - texture_mean
    - *radius_worst
- Danny Top 5 Importance Variables
    - concave.points_worst
    - *concave.points_mean
    - *area_worst
    - *area_mean
    - *radius_worst

## Correlation Plot

```{r}
dataTemp <- read.csv("breast_cancer_diagnostic_data.csv")
datatemp2 <- dataTemp %>% select_if(~ !any(is.na(.)))
dataTot <- datatemp2[,!names(datatemp2) %in% c("id")]

traintemp <- read.csv("training.csv")
trainTot <- traintemp[,!names(traintemp) %in% c("id")]
```

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
dataE <- dataTot
corr_df <- dataE[,c('area_worst', 'area_mean', 'concave.points_mean', 'radius_worst')]
ggpairs(corr_df)
```

## Models

- Calculating Training and Test Set Error
    - Linear Regression
    - Ridge Regression
    - Lasso Regression

## area_mean

![Best Model was Ridge Regression](area_mean.png){width = "50%}

## area_worst

![Best Model was Linear Regression](area_worst.png){width = "50%}

## concave.points_mean
![Best Model was Linear Regression](concave.points_mean.png){width = "50%}

## radius_worst
![Best Model was Linear Regression](radius_worst.png){width = "50%}
